---
title: "Binomial"
author: "Daiki Ina"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial

The package `"binomial"` implements functions for
calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.

## Function bin_choose()

The function bin_choose alculates the number of combinations in which k successes can occur in n trials.

Here’s how you should be able to invoke 'bin_choose()'
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

## Function bin_probability()

The function bin_probability caluclates the probability of an event occuring given the number of success, trials and probability 

Here’s how you should be able to invoke 'bin_probability()'
```{r}
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
## [1] 0.3125
# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
## [1] 0.03125 0.15625 0.31250
# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
```

## Function bin_distribution()

This function returns a data frame with the probability distribution: sucesses in
the first column, probability in the second column.

Here’s how you should be able to invoke 'bin_distribution()'
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

Using 'plot()', a barplot can be graphed to display
the probability histogram of a binomial distribution object "bindis".
```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Function bin_cumulative()

This function returns a data frame with both the probability distribution and the
cumulative probabilities: sucesses in the first column, probability in the second column,
and cumulative in the third column.

Here’s how you should be able to invoke 'bin_cumulative()'
```{r}
# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

Using 'plot()', the cumulative distribution can be graphed in ab object "bincum".
```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


## Function bin_variable()

This function returns an object of class "binvar", that is  a list with named elements:
– trials: number of trials
– prob: probability of success

Here’s an example of how you should be able to invoke bin_variable(), and its printed output:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

The contents of an object "summary.binvar" can be printed as below
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```


## Functions of  measures 

this package also contains main functions for each of the summary
measures: e.g. bin_mean(), bin_variance(), etc.

Here’s how you should be able to invoke these functions
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
